14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-03-24 rules/rules19.tex
Fixed a problem on some URLs that resulted at in at least Mac's preview not understanding that it should open a browser.  Added a reference on opensmt and updated my (Antti's) email.  Wrote a suggestion for the benchmark family description.

\author{%
Liana Hadarean \\
Amazon \\
USA \\
{\small\href{mailto:hadarean@amazon.com}{\texttt{hadarean@amazon.com}}}\\
\and
Antti Hyvarinen \\
Universita della Svizzera italiana \\
Switzerland \\
{\small\href{mailto:tjark.weber@it.uu.se}{\texttt{tjark.weber@it.uu.se}}} \\
\and
Aina Niemetz \\
Stanford University\\
USA\\
{\small\href{mailto:niemetz@cs.stanford.edu}{\texttt{niemetz@cs.stanford.edu}}}\\
\and
Giles Reger \\
University of Manchester \\
UK \\
{\small\href{mailto:giles.reger@manchester.ac.uk}{\texttt{giles.reger@manchester.ac.uk}}} \\
\\
}

@@

\begin{itemize}
\item SMT-COMP mailing list:
  \href{mailto:smt-comp@cs.nyu.edu}{\texttt{smt-comp@cs.nyu.edu}}
\item Sign-up site for the mailing list:
  \url{cs.nyu.edu/mailman/listinfo/smt-comp}
\end{itemize}

\noindent Additional material will be made available at the
competition web site, \url{www.smtcomp.org}.

@@

The annual Satisfiability Modulo Theories Competition~(SMT-COMP) is
held to spur advances in SMT solver implementations on benchmark
formulas of practical interest.  Public competitions are a well-known
means of stimulating advancement in software tools.  For example, in
automated reasoning, the CASC and SAT competitions for first-order and
propositional reasoning tools, respectively, have spurred significant
innovation in their fields~\cite{leberre+03,PSS02}.  More information
on the history and motivation for SMT-COMP can be found at the
competition web site, \url{www.smtcomp.org}, and in reports on
previous
competitions~(\cite{SMTCOMP-JAR,SMTCOMP-FMSD,BDOS08,SMTCOMP-2008,CDW14,SMTCOMP-2012,CSW15}).

@@

\header{Benchmark demographics. \rem{TODO: update}}
%
In SMT-LIB, benchmarks are organized according to \emph{families}.  A
benchmark family contains problems that are similar in some
significant way.  Typically they come from the same source or
application, or are all output by the same tool.  Each top-level
subdirectory within a division represents a distinct family.

@@

\header{Disclosure.}
%
Liana Hadarean was part of the developing team of the SMT solver
CVC4~\cite{cvc4} and is currently not associated with any group
creating or submitting solvers.
Aina Niemetz is part of the developing teams of the SMT solvers
Boolector~\cite{boolector}
and CVC4~\cite{cvc4}.
Antti Hyvarinen is part of the developing team of the SMT solver OpenSMT
\rem{TODO: cite OpenSMT}.
Giles Reger is associated with the group
producing the Vampire system~\cite{vampire}.

>>>>

\author{%
Liana Hadarean \\
Amazon \\
USA \\
{\small\href{mailto:hadarean@amazon.com}{\texttt{hadarean@amazon.com}}}\\
\and
Antti Hyvarinen \\
Universita della Svizzera italiana \\
Switzerland \\
{\small\href{mailto:antti.hyvaerinen@usi.ch}{\texttt{antti.hyvaerinen@usi.ch}}} \\
\and
Aina Niemetz \\
Stanford University\\
USA\\
{\small\href{mailto:niemetz@cs.stanford.edu}{\texttt{niemetz@cs.stanford.edu}}}\\
\and
Giles Reger \\
University of Manchester \\
UK \\
{\small\href{mailto:giles.reger@manchester.ac.uk}{\texttt{giles.reger@manchester.ac.uk}}} \\
\\
}

@@

\begin{itemize}
\item SMT-COMP mailing list:
  \href{mailto:smt-comp@cs.nyu.edu}{\texttt{smt-comp@cs.nyu.edu}}
\item Sign-up site for the mailing list:
  \url{http://cs.nyu.edu/mailman/listinfo/smt-comp}
\end{itemize}

\noindent Additional material will be made available at the
competition web site, \url{http://www.smtcomp.org}.

@@

The annual Satisfiability Modulo Theories Competition~(SMT-COMP) is
held to spur advances in SMT solver implementations on benchmark
formulas of practical interest.  Public competitions are a well-known
means of stimulating advancement in software tools.  For example, in
automated reasoning, the CASC and SAT competitions for first-order and
propositional reasoning tools, respectively, have spurred significant
innovation in their fields~\cite{leberre+03,PSS02}.  More information
on the history and motivation for SMT-COMP can be found at the
competition web site, \url{http://www.smtcomp.org}, and in reports on
previous
competitions~(\cite{SMTCOMP-JAR,SMTCOMP-FMSD,BDOS08,SMTCOMP-2008,CDW14,SMTCOMP-2012,CSW15}).

@@

\header{Benchmark demographics. \rem{TODO: check}}
%
The set of all SMT-LIB benchmarks in a given division can be naturally
partitioned to sets containing benchmarks that are similar from the user
community perspective.  Such benchmarks could all come from the same
application domain, be generated by the same tool, or have some other
obvious common identity.
%
The organizers try to identify a meaningful partitioning based on the
directory hierarchy in SMT-LIB.  In many cases the hierarchy consists of
the top-level directories each corresponding to a submitter, who has
further imposed a hierarchy on the benchmarks.
%
The organizers believe that the submitters have the best information on
the common identity of their benchmarks and therefore partition each
division based on the bottom-level directory imposed by each submitter.
These partitions are referred to as \emph{families}.

@@

\header{Disclosure.}
%
Liana Hadarean was part of the developing team of the SMT solver
CVC4~\cite{cvc4} and is currently not associated with any group
creating or submitting solvers.
Aina Niemetz is part of the developing teams of the SMT solvers
Boolector~\cite{boolector}
and CVC4~\cite{cvc4}.
Antti Hyvarinen is part of the developing team of the SMT solver
OpenSMT~\cite{opensmt2}.
Giles Reger is associated with the group
producing the Vampire system~\cite{vampire}.
